Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
Biproducts.
Say what zero morphism and addition of morphisms is.
CMon-enriched category.

@@

>>>>

\subsection{$\CMon$-enriched category}

A category is $\CMon$-enriched if $\Hom{A}{B}$ is closed under the \emph{zero} morphism $\zero_{A,B}$ and
addition of morphisms $+_{A,B}$ satisfying the commutative monoid laws.

@@

\subsection{Biproducts}

Suppose $C$ a $\CMon$-enriched category. For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an
object $A \oplus B$ of $C$ together with morphisms

\begin{center}
\begin{tikzcd}
   A \arrow[r, "i_A", shift left] &
   A \oplus B \arrow[l, "p_A", shift left] \arrow[r, "p_B"', shift right] &
   B \arrow[l, "i_B"', shift right]
\end{tikzcd}
\end{center}

\noindent satisfying

\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_A \after i_A &= \id_A \\
   p_B \after i_A &= \zero_{A,B}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_B \after i_B &= \id_B \\
   p_A \after i_B &= \zero_{B,A}
\end{salign*}
\end{center}
\end{minipage}

\noindent and

\begin{salign*}
i_A \after p_A + i_B \after p_B &= \id_{A \oplus B}
\end{salign*}
